### 2020-06-08 README.Rmd
readme and removed draft

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Travis build status](https://travis-ci.com/c1au6i0/covid19census_dev.svg?token=PM6d4w2yt4HVWw7s2Jgy&branch=dev)
[![Codecov test coverage](https://codecov.io/gh/c1au6i0/covid19census/branch/master/graph/badge.svg)](https://codecov.io/gh/c1au6i0/covid19census?branch=master)
<!-- badges: end -->

@@

```{r intallation2, eval=FALSE, include=TRUE}
# the repo at the moment private so you need to be authorized 
# don't share the token
library(devtools)

>>>>

<!-- badges: start -->
[![](https://img.shields.io/badge/devel%20version-0.0.0.9600-blue.svg)](https://codecov.io/gh/c1au6i0/covid19census?branch=dev)
[![Travis build status](https://travis-ci.com/c1au6i0/covid19census_dev.svg?token=PM6d4w2yt4HVWw7s2Jgy&branch=dev)
[![Codecov test coverage](https://codecov.io/gh/c1au6i0/covid19census/branch/master/graph/badge.svg)](https://codecov.io/gh/c1au6i0/covid19census?branch=dev)
<!-- badges: end -->

@@

```{r intallation2, eval=FALSE, include=TRUE}
# the repo at the moment is private so you need to be authorized 
# don't share the token
library(devtools)
